---
title: "ggvis"
author: "DataCamp"
output: html_document
runtime: shiny
---
Have you ever wondered whether there is a clear correlation between the gas consumption of a car and its weight?
To answer this question, we first have to load the `dplyr` and `ggvis` packages.

```{r message = FALSE}
library(dplyr)
library(ggvis)
```

```{r chained, results = 'hide'}
mtcars %>%
  group_by(factor(cyl)) %>%
  ggvis(~mpg, ~wt, fill = ~cyl) %>%
  layer_points()
```

The `ggvis` plot gives us a nice visualization of the `mtcars` data set:

```{r ref.label='chained', echo = FALSE}
```



ggvis provides a number of ways to enhance plots with interacticity. For example, the density plot below allows users to set the kernel and bandwidth of the plot.

```{r echo = FALSE, message = FALSE}
library(ggvis)

mtcars %>% ggvis(x = ~wt) %>%
    layer_densities(
      adjust = input_slider(.1, 2, value = 1, step = .1, label = "Bandwidth adjustment"),
      kernel = input_select(
        c("Gaussian" = "gaussian",
          "Epanechnikov" = "epanechnikov",
          "Rectangular" = "rectangular",
          "Triangular" = "triangular",
          "Biweight" = "biweight",
          "Cosine" = "cosine",
          "Optcosine" = "optcosine"),
        label = "Kernel")
    )
```